%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	a4paper, % Uncomment for A4 paper size (default is US letter)
    10pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class


% \usepackage[familydefault,light]{Chivo} %% Option 'familydefault' only if the base font of the document is to be sans serif
% \usepackage[T1]{fontenc}


% \usepackage[sfdefault]{inter} %% Option 'sfdefault' only if 'inter' is to be
% % the base font of the document
% \usepackage[T1]{fontenc}


% \usepackage[defaultfam,tabular,lining]{montserrat} %% Option 'defaultfam'
% %% only if the base font of the document is to be sans serif
% \usepackage[T1]{fontenc}
% \renewcommand*\oldstylenums[1]{{\fontfamily{Montserrat-TOsF}\selectfont #1}}

% \usepackage{nunito}
% \usepackage[T1]{fontenc}


% \usepackage[default,oldstyle,scale=0.95]{opensans} %% Alternatively
% %% use the option 'defaultsans' instead of 'default' to replace the
% %% sans serif font only.
% \usepackage[T1]{fontenc}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

%------------------------------------------------

\name{Anurag Parida} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.
\address{\parbox{0.83\textwidth}{AI-focused full-stack engineer with startup, research, and enterprise experience; passionate about systems, LLMs, and product thinking.}}

\address{Böblinger Straße 156 \\ 70199 Stuttgart, Germany} % Main address

\address{+49 (176)~568~00863 \\ hi@anuragparida.com} % Contact information

% \link{linkedin.com/in/anuragparida \\ github.com/anuragparida}
% \link{www.anuragparida.com}
\link{www.anuragparida.com \\ linkedin.com/in/anuragparida}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

	\textbf{Technische Hochschule Würzburg-Schweinfurt} \hfill \textit{October 2022 - Expected: October 2025} \\
	Bachelors of Engineering in Robotics (English)

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{Final Thesis, Mercedes-Benz Group AG}{April 2025 - Present}{AI and Data Engineering}{Stuttgart, Germany}
		\item Topic: Radical standardisation in corporate software development via LLM-based similarity search.
		\item Working with vector embeddings and databases, OpenAI and Gemini SDKs, BERTopic, HDBSCAN and TF-ID to accelerate planning cycles and reduce redundant app proposals via intelligent and more understandable artifact search.
	\end{rSubsection}

	%------------------------------------------------

	\begin{rSubsection}{Intern, Mercedes-Benz Group AG}{October 2024 - March 2025}{Data Science and Engineering}{Stuttgart, Germany}
		\item Worked in the new MB.OS department to create a new dev-tracking dashboard system for 8000+ colleagues including executives, aimed at increasing bug-fixing and iteration speed by 30\% over traditional AGILE.
		\item Created a portal with 4+ aggregated data vendors including PowerBI, Jira and vehicular data with Grafana to monitor daily performance of different teams and departments under a new proprietary governance structure.
	\end{rSubsection}

	%------------------------------------------------

	\begin{rSubsection}{Research Assistant, THWS}{October 2023 - May 2024}{Application and Architecture Developer}{Schweinfurt, Germany}
		\item Overhauled e-learning UX to improve learning goal tracking; grounded in data with 75\%+ positive user feedback.
		\item Created 3 new authenticated data pipelines, combined performance graphs and personalised learning suggestions.
	\end{rSubsection}

	%------------------------------------------------

	\begin{rSubsection}{Employee \#1, Zepto (KiranaKart, YC SS21)}{November 2020 - February 2021}{Product and Engineering Lead}{Mumbai, India}
		\item Created the systems and front-facing apps for a Y-Combinator startup as the first employee of the founding team. Conducted 50+ field interviews with shopkeepers and residents to validate business plan and market fit.
		\item Scaled the startup from 0 to 100K+ downloads; helped raise \$60M in the process. Helped hire the executive team before leaving to finish my education. The startup later pivoted into a unicorn and scaled nationally as Zepto.
	\end{rSubsection}

    %------------------------------------------------

	\begin{rSubsection}{Software Developer, Flamecloud LLC}{May 2020 - August 2022}{Full-stack Web and Mobile (Freelance)}{Gurgaon, India}
		\item Developed MERN and React Native applications over 2 years in project-based work for a boutique digital agency.
		\item Designed and implemented systems and architectures for 5+ clients including a large Indian e-Bike manufacturer.
	\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Languages   & Python, Typescript, SQL, MERN Stack, React Native                       \\
		Frameworks  & Databricks, Neural Networks, Langchain, Vectors and RAG, LLMs and NLP                 \\
		Tools       & Git, Postman, AWS/GCP/Azure, Jupyter, CI/CD, Docker, Kubernetes, Twilio                               \\
		Interpersonal & Leadership, Problem Solving, Conflict Resolution					\\
		Languages  & English (Native/C2), German (B2), Hindi/Urdu (Native), Odia (Mother Tongue)
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Languages SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Languages}

% 	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{\hspace{6ex}} >{\bfseries}l @{\hspace{6ex}} l @{}}
% 		English    & Native (C2) & German & Intermediate (B2) and getting better! \\
% 		Hindi/Urdu & Native      & Odia   & Mothertongue      \\
% 	\end{tabular}

% \end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Honors and Awards}

	\begin{achSubsection}{Google Code-in Grand Prize Winner + Mentor for Google Summer of Code}{October 2018 - August 2021}
		\item 1 among 54 winners (from 3124 participants) for Google's annual high school programming competition for the SCoReLAB organisation. Got flown out to Google HQ, Mountain View on an all-expense paid trip.
	\end{achSubsection}

	%------------------------------------------------

	% \begin{achSubsection}{Winner at the CBSE National Science Fair}{January 2020}
	% 	\item Project 'ALM8' - Alzheimer's Mate was selected as the winner among 10000+ schools across India in the final round of category 'Assitive Technology'.
	% \end{achSubsection}

	%------------------------------------------------

	\begin{achSubsection}{Grand Finalist at HackHarvard MLH by Alibaba Tianchi}{January 2019}
		\item Invited by Alibaba Tianchi to present my project 'ALM8 - Alzheimer's Mate' at Harvard University during MLH week 2019. Selected in the top 3 of 500+ open bracket participants on the platform 'Codechef'.
	\end{achSubsection}

	%------------------------------------------------

	\begin{achSubsection}{Bronze Medal, International Olympiad in Linguistics Camp by Microsoft}{May 2019}
		\item Chosen among 30 students among 400 applicants across India to attend a 14 day training camp at IIIT Hyderabad, India hosted by Microsoft in computational and socio-linguistics, semantics, NLP and morphology.
	\end{achSubsection}

\end{rSection}

% \begin{rSection}{Hobbies}

% 	Travelling, Bouldering, Snooker, Cricket, Kabaddi


% \end{rSection}

\end{document}
